QCL: Added value of differential correlation

### 2011-12-16 inst/doc/article.Rnw
Reasonable time for testing

<<echo=FALSE,results=hide>>=
  require(qcl)
  set.seed(200)
  data(ath.metabolites) # Arabidopsis Thaliana dataset
  cat("QCL scan\n")
  qcl_result <- QCLscan(ath.metab$genotypes, ath.metab$phenotypes)
  cat("QTL scan\n")
  qtl_result <- QTLscan(ath.metab$genotypes, ath.metab$phenotypes)
  cat("QCL permutation\n")
  qcl_perms1 <- QCLpermute(ath.metab$genotypes, ath.metab$phenotypes, 1:3, 200, n.cores = 3)
  qcl_perms2 <- QCLpermute(ath.metab$genotypes, ath.metab$phenotypes, 4:24, 50, n.cores = 3)
  qcl_perms <- c(qcl_perms1,qcl_perms2)
  #qcl_perms <- vector("list",24)
  #idx <- 1
  #for(p in 1:24){
  #  qcl_perms[[idx]] <- read.QCLpermute("permutations", p, 300,TRUE)
  #  idx <- idx+1
  #}
@

>>>>

<<echo=FALSE,results=hide>>=
  require(qcl)
  set.seed(200)
  data(ath.metabolites) # Arabidopsis Thaliana dataset
  cat("QCL scan\n")
  qcl_result <- QCLscan(ath.metab$genotypes, ath.metab$phenotypes, 1:24, n.perm=250)
@
